Analyzing tomographic images in Python with scikit-image

### 2016-08-17 skimage_tomo.tex
More work on first steps section

\textcolor{blue}{text to be written to explain the following snippets of
code}

\begin{lstlisting}
>>> from skimage import filters
>>> im_gaussian = filters.gaussian(im)
\end{lstlisting}

\begin{lstlisting}
>>> im_gaussian = filters.gaussian(im, sigma=3, mode='wrap')
\end{lstlisting}

\begin{lstlisting}
>>> from skimage import morphology
>>> labels = morphology.watershed(im, markers)
\end{lstlisting}

Most functions take indifferently 2-D or 3-D images as arguments, so that
the same functions can be used to process tomography and microscopy
images. Only a few functions do not support 3-D images and raise an error
when passed a 3-D argument:

\begin{lstlisting}
>>> filters.prewitt(im)
[...]
ValueError: The parameter `image` must be a 2-dimensional array
\end{lstlisting}

>>>>

\texttt{scikit-image} has a very simple API, based almost only on
functions. Most functions take an image (\emph{i.e} a multi-dimensional
array) as input parameter:
\begin{lstlisting}
>>> from skimage import filters
>>> im_gaussian = filters.gaussian(im)
\end{lstlisting}

Optional parameters can be passed as Python's \emph{keyword arguments},
in addition to the image parameter.
\begin{lstlisting}
>>> im_gaussian = filters.gaussian(im, sigma=3, mode='wrap')
\end{lstlisting}
A few functions require several arrays to be passed, such as the
watershed segmentation algorithm that takes as parameters the image to be
segmented, and an image of markers from which labels are propagated:
\begin{lstlisting}
>>> from skimage import morphology
>>> labels = morphology.watershed(im, markers)
\end{lstlisting}
Therefore, the image processing workflow can be considered as a directed graph
(\textcolor{blue}{or is it a tree?})
(rather than a linear pipeline), where nodes are image-shaped arrays, and
edges are functions of \texttt{scikit-image} transforming the arrays (see
Fig.~\ref{fig:ecosystem}).

Most functions take indifferently 2-D or 3-D images as arguments, so that
the same functions can be used to process tomography and microscopy
images. Only a few functions do not support 3-D images and raise an error
when passed a 3-D argument:
\begin{lstlisting}
>>> filters.prewitt(im)
[...]
ValueError: The parameter `image` must be a 2-dimensional array
\end{lstlisting}
